---
title: "SponsorEval"
author: "Mark Walter"
date: "2024-03-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.table.format = "html") 
library(knitr)
library(tidyverse)
library(kableExtra)
```


```{r echo=FALSE}
sponsor <- sponsors[i]
project <- projects[i]
```



Dear `r sponsor`, thank you for sponsoring _`r project`_ for MAE151B this quarter. We need your sponsor evaluation by Tuesday afternoon so we can post grades on time.

In addition to their final prototype, the team's final course deliverable was a design report documenting their work for the quarter AND including all relevant information you have asked for. It was due last Friday; they were told to share it with you. If you did not receive it, make sure you ask them for it.

Please evaluate your team by filling out this short form: https://forms.gle/YKXqaVTQJ59TpKXaA

Considering their participation, communication, contribution, creativity, etc., please evaluate and rate each student by placing an 'X" in your reply e-mail for each row of the following table:

```{r echo=FALSE}
evaltable %>%
  kbl() %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```


Thank you again, and please let us know if you have any questions. 

regards, mark


